### 2016-03-29 chapters/background.tex
refined conclusion, minor fixes

\subsection{Product Configuration}
The variability of a product line is represented by it's feature model, which itself is a set of features with specific interrelations. The configuration process of a product line describes the steps to derive a product from the product line. To archive this, a user has to select a subset of all the possible features within the product line to meet his requirements \cite{vrt}{\color{red} (nicht in Literaturliste)}. However, not all subsets of features result in a valid product. The interrelations of the features restrict the possible combinations of features resulting in a \textit{valid} configuration. {\color{red} Bin mir nicht sicher, was du damit sagen willst... umformulieren?} If only one of the requirements from the interrelations between the features is validated, no product can be created and the configuration as such is considered \textit{invalid}. For an automatic validity check, see the next section.

>>>>

\subsection{Product Configuration}
The variability of a product line is represented by it's feature model, which itself is a set of features with specific interrelations. The configuration process of a product line describes the steps to derive a product from the product line. To archive this, a user has to select a subset of all the possible features within the product line to meet his requirements \cite{vrt}. However, not all subsets of features result in a valid product. The interrelations of the features restrict the possible combinations of features. Thus, not all arbitrary cobinations of features result in a \textit{valid} configuration. If only one of the requirements from the interrelations between the features is validated, no product can be created and the configuration as such is considered \textit{invalid}. For an automatic validity check, see the next section.

### 2016-03-29 chapters/concept.tex
Added/solved reviews part 2/2
refined conclusion, minor fixes

This chapter describes the general workflow we propose within this work. This workflow can be seen in Figure~\ref{img-workflow}. To start off, some kind of software product line is required. It's source code has to be structured in a way that allows for an algorithm to recognize the individual features as well as their interrelations, as these can be very costly to implement by hand.

{\color{red} Pfeil von Fragebogen zu Generator sollte zu der Selektion zeigen.}

@@

Another error we found is one or more features having a parent feature which doesn't exist as a code artifact itself. Thus, the parent feature doesn't exists in the feature model and it's child features can't be placed in the hierarchy in the correct place. To still include these features in the feature model we create an {\color{red}abstract feature (Zitat)} for the parent feature. The abstract feature is a direct child of the root feature. As it doesn't have any describing code, it only has a name and no additional descriptive details.

>>>>

This chapter describes the general workflow we propose within this work. This can be seen in Figure~\ref{img-workflow}. To start off, some kind of software product line is required. It's source code has to be structured in a way that allows for an algorithm to recognize the individual features as well as their interrelations, as these can be very costly to implement by hand.

@@

Another error we found is one or more features having a parent feature which doesn't exist as a code artifact itself. Thus, the parent feature doesn't exists in the feature model and it's child features can't be placed in the hierarchy in the correct place. To still include these features in the feature model we create an {\color{red}abstract feature (Zitat: fospl, page 35, line 10)} for the parent feature. The abstract feature is a direct child of the root feature. As it doesn't have any describing code, it only has a name and no additional descriptive details.

### 2016-03-29 chapters/conclusion.tex
refined conclusion, minor fixes

In this work we propose a questionnaire-based approach to support the process of configuring an existing software product line to generate an actual product. To do so, we use feature models as formalism to structure the existing code artifacts. The feature model gets filled with the information we get from analyzing the structure and conventions of the existing source code. The resulting feature model contains every code artifact as a feature and also includes the constraints and restrictions.

We also introduce a questionnaire to support the configuration of a product from the given product line. A questionnaire needs to be designed carefully by the developers or experts on the domain of the product line. It allows a mapping between answers to simple questions and actual features of the product line. With this method, a user doesn't have to undergo the process of configuration in the sense of \mbox{(de-)selecting} a specific set of features. Instead, the user only has to answer questions according to its use case to do the configuration of his specific product. As the tool uses the underlying FeatureIDE, it also makes use of its functions, such as validity checks. This additionally supports the usability and correctness of the whole process.

%TODO: wann ist es sinnvoll, wann nicht?
%TODO: ist das auf andere Projekte übertragbar? Was sind Voraussetzungen?
%TODO: Threats to Validity

To make meaningful use of the tools introduced in this work, a developer would at least need a software which is structured in a ``feature-like'' manner. This structure has to be in a way that allows a feature model to be extracted from it. Alternatively, this first step can be skipped, if a feature model already exists for the given software product line.

Also, the features need to have some kind of interrelations that allows abstract questions to map to them. If that is not the case, the questionnaire degenerates to a simple (un-) selection of each feature.

>>>>

In this work we propose a questionnaire-based approach to support the process of configuring an existing software product line to generate an actual product. To do so, we use feature models as formalism to structure the existing code artifacts. The feature model automatically gets filled with the information we get from analyzing the structure and conventions of the existing source code. The resulting feature model contains every code artifact as a feature and also includes the constraints and restrictions.

We also propose a questionnaire to support the configuration of a product from the given product line. We introduce definitions in XML, which allow for creation of questionnaires specifically designed for configuration. A questionnaire needs to be designed carefully by the developers or experts on the domain of the product line. It allows a mapping between answers to simple questions and actual features of the product line. With this method, a user doesn't have to undergo the process of configuration in the sense of \mbox{(de-)selecting} a specific set of features. Instead, the user only has to answer questions according to its use case to do the configuration of his specific product. As the tool uses the underlying FeatureIDE, it also makes use of its functions, such as validity checks. This additionally supports the usability and correctness of the whole process.

For the exapmle of \textit{Odoo}, we were able to extract a feature model from the code. We also designed an examplary questionnaire and ran it with a simulated test user. This test user had a certain use case, which we were able to apply to the questionnaire through just answering the presented questions. As a result we got a custom tailored version of \textit{Odoo} for our test user.
